Consistency scores in text data

### 2020-07-08 outputs/documents/paper.Rmd
uploaded literatures
more literatures and one-liners of currently reading articles
added literature about generative pre-training

@@

>>>>

### Article: Improving Language Understanding by Generative Pre-Training (2018)
Introduction of a semi-supervised approach for language understanding machine learning tasks. The approach is the combinaiton of unsupervised pre-training and supervised fine-tuning.

OpenAI GPT-3 is

@@

### Article: Class-Based n-gram Models of Natural Language (1992)
Syntax-based (grammartical) and semantic-based (sensible) word classifications in n-gram models.

### Article: A Statistical Approach to Automatic OCR Error Correction in Context (1996)
Context-sensitive correction system to both non-word and real-word errors based on n-gram models applied to OCR postprocessing.

### Article: Unsupervised Learning of Sentence Embeddings using Compositional n-Gram Features (2017)
Embedding of sentences (sequence of words with semantic representations) compositional n-gram features.
